Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-07-19 awipev-CO2.Rmd

#plot for POSTER june 2019
#plot of S/T
poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
  geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
  labs(x = "Time", y="Temperature (°C)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
print(poster_temp)
#
png("figures/poster_sal_temp.png", width= 1100, height=600)
par(mar=c(5, 4, 4, 6) + 0.1)
#
plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
#
   grid(lty=1)
#
   par(new = T)
#
plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
mtext("",side=1,col="black",line=1.5, cex=1.8)
legend("topleft", legend=c("Temperature (°C)", "Salinity"),
       col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
  grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
    lwd = "months")
     box()
     dev.off()

ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
#
poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
  geom_point(col="blue", size=0.5 )+
  labs(x = "Time", y="Salinity (PSU)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_sal)
ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

#plot for POSTER june 2019
#plot of TA calculated from S + discrete
p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
  geom_point(col="blue", size=0.5 )+
  geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
  labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
  theme(legend.position= c(0.5, 0.93),
                     legend.text=element_text(size=15),
                     plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
                     axis.text=element_text(size=15),
                     axis.title.x= element_text(size =15),
                     legend.title=element_blank())

print(p_at_sal)
ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

#plot for POSTER june 2019
#plot of pCO2

#  add pCO2 atmospheric data from URL

noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
noaa <- noaa %>%
  dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
  unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
  unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
  unite("datetime", c("date", "time"), sep=" ")

noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
noaa <- noaa %>%
 dplyr::filter(datetime > "2015-07-01 00:00:00")

#create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
          expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
           "Calculated from AT/CT"

          )

col <- c("blue","black","red")

poster_pco2 <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
  geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
  geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
  scale_shape_discrete(labels=lab, guide="none")+
  scale_colour_manual(labels=lab, values=col)+
  labs(x = "", y ="", title = "") +
  theme_bw() +
  scale_x_datetime(minor_breaks  = "1 month ")+
  theme(legend.position="top",  #c(0.18, 0.85)
                     legend.text=element_text(size=14, colour="black"),
                     #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
                     axis.text=element_text(size=15),
                     plot.margin = unit(c(0.5,1,1,1), "cm"),
                     axis.title.x= element_text(size =15),
                     legend.title=element_blank()
                     )
print(poster_pco2)
  ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")

@@

#plot for POSTER june 2019
#plot of pH durafet
 poster_dur <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
  labs(x = "", y= "", title = expression(pH[T]~durafet)) +
  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
   theme(legend.position= c(0.17, 0.8),
                     legend.text=element_text(size=14),
                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
                      axis.text=element_text(size=15),
                      plot.margin = unit(c(1,1,1,1), "cm"),
                      axis.title.x= element_text(size =15),
                      legend.title=element_blank())

print(poster_dur)
ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")

@@

### **FerryBox**
- **2019-06-05**: PRoblem in the relay 15 that controls the waste water pump was found. The spare part will be brought here next week (when Samir will leave...).
- **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
- **2019-05-21**: FB is unstable. 
- **2019-04-14**: FB is working again. 
- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
- **2019-02-27**: FB is working again. 
- **2019-02-26**: FB is stopped because of a "leakage" issue. 
- **2019-01-17**: FB is stopped until 19th January 
- **2019-01-11**: FB is stopped until 12th Decmeber. 
- **2018-12-28**: FB is stopped until 31st Decmeber. 
- **2018-10-12**: FB is working again. 
- **2018-10-10**: FB is stopped after a seawater leakage. 
- **2018-10-08**: FB is working again. 
- **2018-10-05**: FB is stopped after a seawater leakage. 
- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
- **2017-03-20**: Philipp arrived in NYA to solve the problem.
- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
- **2016-09-20**: Test in the Ferrybox with the seawater. Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it. This system was installed if the pumps 1 and 2 broke during winter. This is a "plan C". This system is not automatic and we will be informed about its power up in case of emergency. As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
- **2016-09-12**: No data because of maintenance until the 18th.
- **2016-09-10**: No data because of maintenance until the 11th.
- **2016-05-09**: data are back.
- **2016-05-04**: No data for all parameters because of electricity issues. 
- **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.

### **TA analyser**
- **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
- **2019-01-16**: Bad data since this date. 
- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer). Samir received password and access from the AWI in order to communicate from France with the TA.                  
- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
- **2016-05-01**: No data for TA.
- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).

>>>>

# #plot for POSTER june 2019
# #plot of S/T
# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
#   labs(x = "Time", y="Temperature (°C)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
# print(poster_temp)
# #
# png("figures/poster_sal_temp.png", width= 1100, height=600)
# par(mar=c(5, 4, 4, 6) + 0.1)
# #
# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
# #
#    grid(lty=1)
# #
#    par(new = T)
# #
# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
# mtext("",side=1,col="black",line=1.5, cex=1.8)
# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
#   grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
#     lwd = "months")
#      box()
#      dev.off()
# 
# 
# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
# #
# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
#   geom_point(col="blue", size=0.5 )+
#   labs(x = "Time", y="Salinity (PSU)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
# print(poster_sal)
# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

# #plot for POSTER june 2019
# #plot of TA calculated from S + discrete
# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
#   geom_point(col="blue", size=0.5 )+
#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position= c(0.5, 0.93),
#                      legend.text=element_text(size=15),
#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
#                      axis.text=element_text(size=15),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank())
# 
# 
# print(p_at_sal)
# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pCO2
# 
# #  add pCO2 atmospheric data from URL
# 
# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
# noaa <- noaa %>%
#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
#   unite("datetime", c("date", "time"), sep=" ")
# 
# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
# noaa <- noaa %>%
#  dplyr::filter(datetime > "2015-07-01 00:00:00")
# 
# #create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
# lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
#           expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
#            "Calculated from AT/CT"
# 
#           )
# 
# col <- c("blue","black","red")
# 
# poster_pco2 <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
#   geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
#   geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
#   scale_shape_discrete(labels=lab, guide="none")+
#   scale_colour_manual(labels=lab, values=col)+
#   labs(x = "", y ="", title = "") +
#   theme_bw() +
#   scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position="top",  #c(0.18, 0.85)
#                      legend.text=element_text(size=14, colour="black"),
#                      #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
#                      axis.text=element_text(size=15),
#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank()
#                      )
# print(poster_pco2)
#   ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pH durafet
#  poster_dur <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
#   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
#    theme(legend.position= c(0.17, 0.8),
#                      legend.text=element_text(size=14),
#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
#                       axis.text=element_text(size=15),
#                       plot.margin = unit(c(1,1,1,1), "cm"),
#                       axis.title.x= element_text(size =15),
#                       legend.title=element_blank())
# 
# print(poster_dur)
# ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")

@@

### **FerryBox**
- **2019-06-12**: Markus came to do maintenace. 
- **2019-06-05**: Problem in the relay 15 that controls the waste water pump was found. The spare part will be brought here next week (when Samir will leave...).
- **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
- **2019-05-21**: FB is unstable. 
- **2019-04-14**: FB is working again. 
- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
- **2019-02-27**: FB is working again. 
- **2019-02-26**: FB is stopped because of a "leakage" issue. 
- **2019-01-17**: FB is stopped until 19th January 
- **2019-01-11**: FB is stopped until 12th Decmeber. 
- **2018-12-28**: FB is stopped until 31st Decmeber. 
- **2018-10-12**: FB is working again. 
- **2018-10-10**: FB is stopped after a seawater leakage. 
- **2018-10-08**: FB is working again. 
- **2018-10-05**: FB is stopped after a seawater leakage. 
- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
- **2017-03-20**: Philipp arrived in NYA to solve the problem.
- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
- **2016-09-20**: Test in the Ferrybox with the seawater. Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it. This system was installed if the pumps 1 and 2 broke during winter. This is a "plan C". This system is not automatic and we will be informed about its power up in case of emergency. As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
- **2016-09-12**: No data because of maintenance until the 18th.
- **2016-09-10**: No data because of maintenance until the 11th.
- **2016-05-09**: data are back.
- **2016-05-04**: No data for all parameters because of electricity issues. 
- **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.

### **TA analyser**
- **2019-07-12**: Steffen told us that calibration was not OK. To check it, he calculated the mediane of the pH/volume sample / volumeIndicatorfactor and compared them to January/October calibration. We wait for Steffen recommandations before to make another calibration.
- **2019-06-07**: Samir did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. TA was stable before the calibration and calibration was OK.
- **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
- **2019-01-16**: Bad data since this date. 
- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer). Samir received password and access from the AWI in order to communicate from France with the TA.                  
- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
- **2016-05-01**: No data for TA.
- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).
